### 2017-08-25 Paper01_EnthalpyAndCrystallization.tex
Results - Dynamic XRD - added normalised figures

>>>>

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_185.png}
	\caption[Table of contents Capition]{Normalised dynamic \acrshort{xrd} from $150-185$\degree C. Large bulk peaks have been faceted as to not dwarf smaller peaks and details.}%global caption
	\label{fig:XRD_Dynamic_185}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_145.png}
	\caption[Table of contents Capition]{Normalised dynamic \acrshort{xrd} from $110-145$\degree C.}%global caption
	\label{fig:XRD_Dynamic_145}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Dynamic_105.png}
	\caption[Table of contents Capition]{Normalised dynamic \acrshort{xrd} from $35-105$\degree C.}%global caption
	\label{fig:XRD_Dynamic_105}
\end{figure}
